### 2023-11-15 Scripts/Manuscript/manuscript.Rmd
added some missed R references.

# manually retrieving the Rstudio version
RStudio.Version()
```

@@

The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio XXXRSTUDIOREFERENCEHEREXXX. with R version 4.2.2 XXXRREFERENCEHEREXXX. Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information formed the replication datasets in the analysis.

>>>>

# manually retrieving the Rstudio version
rstudioapi::versionInfo()
```

@@

The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information formed the replication datasets in the analysis.
